Identification of high-yielding soybean lines with exceptional seed composition qualities

### 2022-07-12 doc/manuscript/manuscript.tex
Small changed to the manuscript.docx document

A strong negative correlation (r = -0.93) was observed in both tests
between seed protein and seed oil content. A weak negative correlation
(r = -0.29) was observed between seed protein and yield in both tests
which was statistically insignificant in either population. Weak
positive correlations were also observed between seed oil and seed yield
in both populations. A correlation coefficient of r = 0.24 was observed
in Test 1 while a coefficient of r = 0.28 was observed in Test 2. These
correlation coefficients were not statistically significant in either
population. The pairwise correlation coefficients for Tests 1 and 2 are
presented in supplementary figures 2 and 3, respectively.

\begin{figure}[H]
\centering
\includegraphics[width=15 cm]{C:/Users/jhgille2/Documents/R/projects/Jay_yield/exports/plots/lsmean_scatterplot.pdf}
\caption{Genotype Least square means for seed oil, seed protein, and seed yield for soybean RILs in Test 1 (\textbf{A}) and Test 2 (\textbf{B}). Points indicate the least square means and error bars indicate the standard errors in the estimation of least square means. Blue dots indicate that a RIL has a least square mean above the average of the checks in the test and a color of red indicates that the RIL has a mean value below the check average. The check average is shown with the vertical dashed line.}
\end{figure}

@@

\caption{Soybean genotypes with yield and seed oil comparable to check cultivars, and seed protein superior to check cultivars.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lllrlllrlllrll}
\toprule
\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{4}{c}{Protein} & \multicolumn{4}{c}{Yield} & \multicolumn{4}{c}{Oil} \\
\cmidrule(l{3pt}r{3pt}){3-6} \cmidrule(l{3pt}r{3pt}){7-10} \cmidrule(l{3pt}r{3pt}){11-14}
Genotype & Test Name & Value & Rank & Test Average & Check Average & Value & Rank & Test Average & Check Average & Value & Rank & Test Average & Check Average\\
\midrule
N18-1635 & Jay Test 1 & 43.61 (106.5\%) & 16 & 45.09 & 40.94 & 46.45 (103.1\%) & 4 & 42.92 & 45.05 & 21.72 (96.7\%) & 3 & 20.89 & 22.45\\
\cmidrule{1-14}
N18-1783 &  & 46.74 (109.3\%) & 8 &  &  & 37.63 (86.6\%) & 19 &  &  & 20.63 (96.5\%) & 11 &  & \\
\cmidrule{1-1}
\cmidrule{3-4}
\cmidrule{7-8}
\cmidrule{11-12}
N18-1627 &  & 45.9 (107.3\%) & 9 &  &  & 46.01 (105.9\%) & 8 &  &  & 20.62 (96.5\%) & 12 &  & \\
\cmidrule{1-1}
\cmidrule{3-4}
\cmidrule{7-8}
\cmidrule{11-12}
N18-1643 & \multirow{-3}{*}{\raggedright\arraybackslash Jay Test 2} & 44.35 (103.7\%) & 13 & \multirow{-3}{*}{\raggedright\arraybackslash 45.7} & \multirow{-3}{*}{\raggedright\arraybackslash 42.77} & 40.54 (93.3\%) & 16 & \multirow{-3}{*}{\raggedright\arraybackslash 43.65} & \multirow{-3}{*}{\raggedright\arraybackslash 43.44} & 21.45 (100.4\%) & 7 & \multirow{-3}{*}{\raggedright\arraybackslash 20.7} & \multirow{-3}{*}{\raggedright\arraybackslash 21.37}\\
\bottomrule
\multicolumn{14}{l}{\rule{0pt}{1em}\textsuperscript{*} The genotype name.}\\
\multicolumn{14}{l}{\rule{0pt}{1em}\textsuperscript{\dag} The genotype marginal mean for the phenotype (value divided by check average).}\\
\multicolumn{14}{l}{\rule{0pt}{1em}\textsuperscript{\ddag} The ranking of this genotype for the phenotype within its test.}\\
\multicolumn{14}{l}{\rule{0pt}{1em}\textsuperscript{\S} The average phenotype value for all genotypes in the test.}\\
\multicolumn{14}{l}{\rule{0pt}{1em}\textsuperscript{\P} The average value of the checks in the test.}\\
\end{tabular}}
\end{table}

@@

\caption{Soybean RILs with superior protein content and comparable yield performance to high-yielding check cultivars.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lllrlllrll}
\toprule
\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{4}{c}{Protein} & \multicolumn{4}{c}{Yield} \\
\cmidrule(l{3pt}r{3pt}){3-6} \cmidrule(l{3pt}r{3pt}){7-10}
Genotype & Test Name & Value & Rank & Test Average & Check Average & Value & Rank & Test Average & Check Average\\
\midrule
N18-1763 &  & 47.82 (116.8\%) & 2 &  &  & 39.45 (87.6\%) & 17 &  & \\
\cmidrule{1-1}
\cmidrule{3-4}
\cmidrule{7-8}
N18-1855 &  & 47.52 (116.1\%) & 3 &  &  & 43.17 (95.8\%) & 10 &  & \\
\cmidrule{1-1}
\cmidrule{3-4}
\cmidrule{7-8}
N18-1595 &  & 47.36 (115.7\%) & 4 &  &  & 43.52 (96.6\%) & 9 &  & \\
\cmidrule{1-1}
\cmidrule{3-4}
\cmidrule{7-8}
N18-1632-1 &  & 46.64 (113.9\%) & 6 &  &  & 45.73 (101.5\%) & 6 &  & \\
\cmidrule{1-1}
\cmidrule{3-4}
\cmidrule{7-8}
N18-1620 &  & 43.63 (106.6\%) & 15 &  &  & 46.54 (103.3\%) & 3 &  & \\
\cmidrule{1-1}
\cmidrule{3-4}
\cmidrule{7-8}
N18-1635 &  & 43.61 (106.5\%) & 16 &  &  & 46.45 (103.1\%) & 4 &  & \\
\cmidrule{1-1}
\cmidrule{3-4}
\cmidrule{7-8}
N18-1731 &  & 46.1 (112.6\%) & 8 &  &  & 43.16 (95.8\%) & 11 &  & \\
\cmidrule{1-1}
\cmidrule{3-4}
\cmidrule{7-8}
N18-1674 &  & 45.19 (110.4\%) & 9 &  &  & 44.26 (98.2\%) & 7 &  & \\
\cmidrule{1-1}
\cmidrule{3-4}
\cmidrule{7-8}
N18-1682 &  & 45.11 (110.2\%) & 10 &  &  & 43.64 (96.9\%) & 8 &  & \\
\cmidrule{1-1}
\cmidrule{3-4}
\cmidrule{7-8}
N18-1572 &  & 45.08 (110.1\%) & 11 &  &  & 38.58 (85.6\%) & 19 &  & \\
\cmidrule{1-1}
\cmidrule{3-4}
\cmidrule{7-8}
N18-1751 & \multirow{-11}{*}{\raggedright\arraybackslash Jay Test 1} & 44.8 (109.4\%) & 12 & \multirow{-11}{*}{\raggedright\arraybackslash 45.09} & \multirow{-11}{*}{\raggedright\arraybackslash 40.94} & 41.59 (92.3\%) & 15 & \multirow{-11}{*}{\raggedright\arraybackslash 42.92} & \multirow{-11}{*}{\raggedright\arraybackslash 45.05}\\
\cmidrule{1-10}
N18-1761 &  & 49.1 (114.8\%) & 2 &  &  & 45.74 (105.3\%) & 9 &  & \\
\cmidrule{1-1}
\cmidrule{3-4}
\cmidrule{7-8}
N18-1575 &  & 48.67 (113.8\%) & 4 &  &  & 42.49 (97.8\%) & 12 &  & \\
\cmidrule{1-1}
\cmidrule{3-4}
\cmidrule{7-8}
N18-1769 &  & 48.58 (113.6\%) & 5 &  &  & 37.88 (87.2\%) & 18 &  & \\
\cmidrule{1-1}
\cmidrule{3-4}
\cmidrule{7-8}
N18-1783 &  & 46.74 (109.3\%) & 8 &  &  & 37.63 (86.6\%) & 19 &  & \\
\cmidrule{1-1}
\cmidrule{3-4}
\cmidrule{7-8}
N18-1627 &  & 45.9 (107.3\%) & 9 &  &  & 46.01 (105.9\%) & 8 &  & \\
\cmidrule{1-1}
\cmidrule{3-4}
\cmidrule{7-8}
N18-1643 & \multirow{-6}{*}{\raggedright\arraybackslash Jay Test 2} & 44.35 (103.7\%) & 13 & \multirow{-6}{*}{\raggedright\arraybackslash 45.7} & \multirow{-6}{*}{\raggedright\arraybackslash 42.77} & 40.54 (93.3\%) & 16 & \multirow{-6}{*}{\raggedright\arraybackslash 43.65} & \multirow{-6}{*}{\raggedright\arraybackslash 43.44}\\
\bottomrule
\multicolumn{10}{l}{\rule{0pt}{1em}\textsuperscript{*} The genotype name.}\\
\multicolumn{10}{l}{\rule{0pt}{1em}\textsuperscript{\dag} The genotype marginal mean for the phenotype (value divided by check average).}\\
\multicolumn{10}{l}{\rule{0pt}{1em}\textsuperscript{\ddag} The ranking of this genotype for the phenotype within its test.}\\
\multicolumn{10}{l}{\rule{0pt}{1em}\textsuperscript{\S} The average phenotype value for all genotypes in the test.}\\
\multicolumn{10}{l}{\rule{0pt}{1em}\textsuperscript{\P} The average value of the checks in the test.}\\
\end{tabular}}
\end{table}

>>>>

A strong negative correlation (r = -0.93) was observed in both tests
between seed protein and seed oil content. A weak negative correlation
(r = -0.29) was observed between seed protein and yield in both tests
which was statistically insignificant in either population. Weak
positive correlations were also observed between seed oil and seed yield
in both populations. A correlation coefficient of r = 0.24 was observed
in Test 1 while a coefficient of r = 0.28 was observed in Test 2. These
correlation coefficients were not statistically significant in either
population. The pairwise correlation coefficients for Tests 1 and 2 are
presented in supplementary figures 1 and 2, respectively.

\begin{figure}[H]
\centering
\includegraphics[width=15 cm]{C:/Users/jhgille2/Documents/R/projects/Jay_yield/exports/plots/lsmean_scatterplot.pdf, C:/Users/jhgille2/Documents/R/projects/Jay_yield/exports/plots/lsmean_scatterplot.png}
\caption{Genotype Least square means for seed oil, seed protein, and seed yield for soybean RILs in Test 1 (\textbf{A}) and Test 2 (\textbf{B}). Points indicate the least square means and error bars indicate the standard errors in the estimation of least square means. Blue dots indicate that a RIL has a least square mean above the average of the checks in the test and a color of red indicates that the RIL has a mean value below the check average. The check average is shown with the vertical dashed line.}
\end{figure}

@@

\caption{Soybean genotypes with yield and seed oil comparable to check cultivars, and seed protein superior to check cultivars.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lllrlllrlllrll}
\toprule
\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{4}{c}{Protein} & \multicolumn{4}{c}{Yield} & \multicolumn{4}{c}{Oil} \\
\cmidrule(l{3pt}r{3pt}){3-6} \cmidrule(l{3pt}r{3pt}){7-10} \cmidrule(l{3pt}r{3pt}){11-14}
Genotype & Test Name & Value & Rank & Test Average & Check Average & Value & Rank & Test Average & Check Average & Value & Rank & Test Average & Check Average\\
\midrule
N18-1635 & Jay Test 1 & 43.61 (106.5\%) & 16 & 45.09 & 40.94 & 46.45 (103.1\%) & 4 & 42.92 & 45.05 & 21.72 (96.7\%) & 3 & 20.89 & 22.45\\
\cmidrule{1-14}
N18-1783 &  & 46.74 (109.3\%) & 8 &  &  & 37.63 (86.6\%) & 19 &  &  & 20.63 (96.5\%) & 11 &  & \\
\cmidrule{1-1}
\cmidrule{3-4}
\cmidrule{7-8}
\cmidrule{11-12}
N18-1627 &  & 45.9 (107.3\%) & 9 &  &  & 46.01 (105.9\%) & 8 &  &  & 20.62 (96.5\%) & 12 &  & \\
\cmidrule{1-1}
\cmidrule{3-4}
\cmidrule{7-8}
\cmidrule{11-12}
N18-1643 & \multirow{-3}{*}{\raggedright\arraybackslash Jay Test 2} & 44.35 (103.7\%) & 13 & \multirow{-3}{*}{\raggedright\arraybackslash 45.7} & \multirow{-3}{*}{\raggedright\arraybackslash 42.77} & 40.54 (93.3\%) & 16 & \multirow{-3}{*}{\raggedright\arraybackslash 43.65} & \multirow{-3}{*}{\raggedright\arraybackslash 43.44} & 21.45 (100.4\%) & 7 & \multirow{-3}{*}{\raggedright\arraybackslash 20.7} & \multirow{-3}{*}{\raggedright\arraybackslash 21.37}\\
\bottomrule
\multicolumn{14}{l}{\rule{0pt}{1em}\textsuperscript{*} The genotype name.}\\
\multicolumn{14}{l}{\rule{0pt}{1em}\textsuperscript{\dag} The test name}\\
\multicolumn{14}{l}{\rule{0pt}{1em}\textsuperscript{\ddag} The genotype marginal mean for the phenotype (value divided by check average).}\\
\multicolumn{14}{l}{\rule{0pt}{1em}\textsuperscript{\S} The ranking of this genotype for the phenotype within its test.}\\
\multicolumn{14}{l}{\rule{0pt}{1em}\textsuperscript{\P} The average phenotype value for all genotypes in the test.}\\
\multicolumn{14}{l}{\rule{0pt}{1em}\textsuperscript{**} The average value of the checks in the test.}\\
\end{tabular}}
\end{table}

@@

\caption{Soybean RILs with superior protein content and comparable yield performance to high-yielding check cultivars.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lllrlllrll}
\toprule
\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{4}{c}{Protein} & \multicolumn{4}{c}{Yield} \\
\cmidrule(l{3pt}r{3pt}){3-6} \cmidrule(l{3pt}r{3pt}){7-10}
Genotype & Test Name & Value & Rank & Test Average & Check Average & Value & Rank & Test Average & Check Average\\
\midrule
N18-1763 &  & 47.82 (116.8\%) & 2 &  &  & 39.45 (87.6\%) & 17 &  & \\
\cmidrule{1-1}
\cmidrule{3-4}
\cmidrule{7-8}
N18-1855 &  & 47.52 (116.1\%) & 3 &  &  & 43.17 (95.8\%) & 10 &  & \\
\cmidrule{1-1}
\cmidrule{3-4}
\cmidrule{7-8}
N18-1595 &  & 47.36 (115.7\%) & 4 &  &  & 43.52 (96.6\%) & 9 &  & \\
\cmidrule{1-1}
\cmidrule{3-4}
\cmidrule{7-8}
N18-1632-1 &  & 46.64 (113.9\%) & 6 &  &  & 45.73 (101.5\%) & 6 &  & \\
\cmidrule{1-1}
\cmidrule{3-4}
\cmidrule{7-8}
N18-1620 &  & 43.63 (106.6\%) & 15 &  &  & 46.54 (103.3\%) & 3 &  & \\
\cmidrule{1-1}
\cmidrule{3-4}
\cmidrule{7-8}
N18-1635 &  & 43.61 (106.5\%) & 16 &  &  & 46.45 (103.1\%) & 4 &  & \\
\cmidrule{1-1}
\cmidrule{3-4}
\cmidrule{7-8}
N18-1731 &  & 46.1 (112.6\%) & 8 &  &  & 43.16 (95.8\%) & 11 &  & \\
\cmidrule{1-1}
\cmidrule{3-4}
\cmidrule{7-8}
N18-1674 &  & 45.19 (110.4\%) & 9 &  &  & 44.26 (98.2\%) & 7 &  & \\
\cmidrule{1-1}
\cmidrule{3-4}
\cmidrule{7-8}
N18-1682 &  & 45.11 (110.2\%) & 10 &  &  & 43.64 (96.9\%) & 8 &  & \\
\cmidrule{1-1}
\cmidrule{3-4}
\cmidrule{7-8}
N18-1572 &  & 45.08 (110.1\%) & 11 &  &  & 38.58 (85.6\%) & 19 &  & \\
\cmidrule{1-1}
\cmidrule{3-4}
\cmidrule{7-8}
N18-1751 & \multirow{-11}{*}{\raggedright\arraybackslash Jay Test 1} & 44.8 (109.4\%) & 12 & \multirow{-11}{*}{\raggedright\arraybackslash 45.09} & \multirow{-11}{*}{\raggedright\arraybackslash 40.94} & 41.59 (92.3\%) & 15 & \multirow{-11}{*}{\raggedright\arraybackslash 42.92} & \multirow{-11}{*}{\raggedright\arraybackslash 45.05}\\
\cmidrule{1-10}
N18-1761 &  & 49.1 (114.8\%) & 2 &  &  & 45.74 (105.3\%) & 9 &  & \\
\cmidrule{1-1}
\cmidrule{3-4}
\cmidrule{7-8}
N18-1575 &  & 48.67 (113.8\%) & 4 &  &  & 42.49 (97.8\%) & 12 &  & \\
\cmidrule{1-1}
\cmidrule{3-4}
\cmidrule{7-8}
N18-1769 &  & 48.58 (113.6\%) & 5 &  &  & 37.88 (87.2\%) & 18 &  & \\
\cmidrule{1-1}
\cmidrule{3-4}
\cmidrule{7-8}
N18-1783 &  & 46.74 (109.3\%) & 8 &  &  & 37.63 (86.6\%) & 19 &  & \\
\cmidrule{1-1}
\cmidrule{3-4}
\cmidrule{7-8}
N18-1627 &  & 45.9 (107.3\%) & 9 &  &  & 46.01 (105.9\%) & 8 &  & \\
\cmidrule{1-1}
\cmidrule{3-4}
\cmidrule{7-8}
N18-1643 & \multirow{-6}{*}{\raggedright\arraybackslash Jay Test 2} & 44.35 (103.7\%) & 13 & \multirow{-6}{*}{\raggedright\arraybackslash 45.7} & \multirow{-6}{*}{\raggedright\arraybackslash 42.77} & 40.54 (93.3\%) & 16 & \multirow{-6}{*}{\raggedright\arraybackslash 43.65} & \multirow{-6}{*}{\raggedright\arraybackslash 43.44}\\
\bottomrule
\multicolumn{10}{l}{\rule{0pt}{1em}\textsuperscript{*} The genotype name.}\\
\multicolumn{10}{l}{\rule{0pt}{1em}\textsuperscript{\dag} The test name}\\
\multicolumn{10}{l}{\rule{0pt}{1em}\textsuperscript{\ddag} The genotype marginal mean for the phenotype (value divided by check average).}\\
\multicolumn{10}{l}{\rule{0pt}{1em}\textsuperscript{\S} The ranking of this genotype for the phenotype within its test.}\\
\multicolumn{10}{l}{\rule{0pt}{1em}\textsuperscript{\P} The average phenotype value for all genotypes in the test.}\\
\multicolumn{10}{l}{\rule{0pt}{1em}\textsuperscript{**} The average value of the checks in the test.}\\
\end{tabular}}
\end{table}
